% Bibliography
\clearpage
\addcontentsline{toc}{chapter}{Bibliografia}
{\footnotesize \bibliographystyle{plain}
\renewcommand{\bibname}{Bibliografia}

\begin{thebibliography}{99}

\bibitem{Abramovich2002}
    Abramovich, Y.\,A., Aliprantis, C.\,D.,
    \emph{Problems in operator theory},
    American Mathematical Society, Rhode Island 2002.

\bibitem{adesso2007entanglement}
    Adesso, G., Illuminati, F.,
    Entanglement in continuous-variable systems: recent advances and current perspectives,
    \emph{J. Phys. A: Math. Gen.} {\bf 40} (2007), 7821.

\bibitem{araki1968classification}
    Araki, H., Woods, E.\,J.,
    A classification of factors,
    \emph{Publ. Res. I. Math. Sci.} {\bf 4} (1968), 51.

\bibitem{besenyei2011completely}
    Besenyei, {\'A}., Petz, D.,
    Completely positive mappings and mean matrices,
    \emph{Linear Algebra Appl.} {\bf 435} (2011), 984.

\bibitem{Blackadar2006}
    Blackadar, B., \emph{Operator Algebras: Theory of C*-algebras and von Neumann Algebras},
    Springer, Berlin Heidelberg New York 2006.

\bibitem{bourennane2004experimental}
    Bourennane, M., \emph{et al.},
    Experimental detection of multipartite entanglement using witness operators,
    \emph{Phys. Rev. Lett.} {\bf 92} (2004), 87902.

\bibitem{Bratteli2003}
    Bratteli, O., Robinson, D.\,W.,
    \emph{Operator Algebras and Quantum Statistical \mbox{Mechanics 1:} C*- and W*-Algebras. Symmetry Groups. Decomposition of States},
    Springer, Berlin Heidelberg New York 2003.

\bibitem{Brown2008}
    Brown, N.\,P., Ozawa, N.,
    \emph{C*-Algebras and Finite-Dimensional Approximations},
    American Mathematical Society, Rhode Island 2008.

\bibitem{choi1975completely}
    Choi, M.-D.,
    Completely positive linear maps on complex matrices,
    \emph{Linear Algebra Appl.} {\bf 10} (1975), 285.

\bibitem{choi1975positive}
    Choi, M.-D.,
    Positive semidefinite biquadratic forms,
    \emph{Linear Algebra Appl.} {\bf 12} (1975), 95.

\bibitem{choi1980some}
    Choi, M.-D.,
    Some assorted inequalities for positive linear maps on C*-algebras,
    \emph{J. Operat. Theor.} {\bf 4} (1980), 271.

\bibitem{choi1977extremal}
    Choi, M.-D., Lam, T.-Y.,
    Extremal positive semidefinite forms,
    \emph{Math. Ann.} {\bf 231} (1977), 1.

\bibitem{chow1975compact}
    Chow, H.\,L.,
    On compact affine semigroups,
    \emph{Semigroup Forum} {\bf 11} (1975), 146.

%\bibitem{chruscinski2011exposed}
%    Chru{\'s}ci{\'n}ski, D., Sarbicki, G.,
%    Exposed positive maps: a sufficient condition,
%    \emph{arXiv preprint} (2012), arXiv:1111.2012.

%\bibitem{Dixmier1981}
%    Dixmier, J., Jellet, F.,
%    \emph{von Neumann algebras}, North-Holland Publishing Company, New York 1981.

\bibitem{Effros2000}
    Effros, E.\,G., Ruan, Z.-J., \emph{Operator Spaces}, Clarendon Press, Oxford 2000.

\bibitem{einstein1935can}
    Einstein, A., \emph{et al.},
    Can quantum-mechanical description of physical reality be considered complete?,
    \emph{Phys. Rev.} {\bf 47} (1935), 777.

\bibitem{Evans1998}
    Evans, D.\,E., Kawahigashi, Y.,
    \emph{Quantum Symmetries on Operator Algebras}, Clarendon Press, Oxford 1998.

\bibitem{goyal2011geometry}
    Goyal, S.\,K. \emph{et al.},
    Geometry of the generalized Bloch sphere for qutrit,
    \emph{arXiv preprint} (2011), arXiv:1111.4427.

\bibitem{ha1998atomic}
    Ha, K.-C.,
    Atomic positive linear maps in matrix algebras,
    \emph{Publ. Res. I. Math. Sci.} {\bf 34} (1998), 591.

\bibitem{ha2011entanglement}
    Ha, K.-C., Kye, S.-H.,
    Entanglement witnesses arising from exposed positive linear maps,
    \emph{Open Syst. Inf. Dyn.} {\bf 18} (2011), 323.

\bibitem{horodecki1996separability}
      Horodecki, M., \emph{et al.},
      Separability of mixed states: necessary and sufficient conditions,
      \emph{Phys. Lett. A} {\bf 223} (1996), 1.

\bibitem{horodecki2009quantum}
    Horodecki, R., \emph{et al.},
    Quantum entanglement,
    \emph{Rev. Mod. Phys.} {\bf 81} (2009), 865.

\bibitem{jamiolkowski1974effective}
      Jamio{\l}kowski, A.,
      An effective method of investigation of positive maps on the set of positive definite operators,
      \emph{Rep. Math. Phys.} {\bf 5} (1974), 415.

\bibitem{jamiolkowski1972linear}
    Jamio{\l}kowski, A.,
    Linear transformations which preserve trace and positive semidefiniteness of operators,
    \emph{Rep. Math. Phys.} {\bf 3} (1972), 275.

\bibitem{kadison1952generalized}
    Kadison, R.\,V.,
    A generalized Schwarz inequality and algebraic invariants for operator algebras,
    \emph{The Annals of Mathematics} {\bf 56} (1952), 494.

\bibitem{kye1995positive}
    Kye, S.-H.,
    Positive linear maps between matrix algebras which fix diagonals,
    \emph{Linear Algebra Appl.} {\bf 216} (1995), 239.

\bibitem{landau1993birkhoff}
    Landau, L.\,J., Streater, R.\,F.,
    On Birkhoff's theorem for doubly stochastic completely positive maps of matrix algebras,
    \emph{Linear Algebra Appl.} {\bf 196} (1993), 107.

\bibitem{leinaas2006geometrical}
    Leinaas, J.\,M., \emph{et al.},
    Geometrical aspects of entanglement,
    \emph{Phys. Rev. A} {\bf 74} (2006), 12313.

\bibitem{loewy1975positive}
    Loewy, R., Schneider, H.,
    Positive operators on the n-dimensional ice cream cone,
    \emph{J.Math. Anal. App.} {\bf 49} (1975), 375.

\bibitem{marciniak2008extremal}
    Marciniak, M.,
    On extremal positive maps acting between type I factors,
    \emph{Banach Center Publications} {\bf 89} (2010), 201.

\bibitem{miller2015extremal}
    Miller, M., Olkiewicz, R.,
    Extremal positive maps on $M_{3}(\mathbb{C})$ and idempotent matrices,
    \emph{arXiv preprint} (2015), arXiv:1510.04920.

\bibitem{miller2014horodeckis}
    Miller, M., Olkiewicz, R.,
    Horodeckis criterion of separability of mixed states in von Neumann and C*-algebras,
    \emph{Infin. Dimens. Anal. Qu.} {\bf 17} (2014), 1450028.

\bibitem{miller2015stable}
    Miller, M., Olkiewicz, R.,
    Stable subspaces of positive maps of matrix algebras,
    \emph{Open Syst. Inf. Dyn.} {\bf 22} (2015), 1550011.

\bibitem{miller2015topology}
    Miller, M., Olkiewicz, R.,
    Topology of the cone of positive maps on qubit systems,
    \emph{J. Phys. A: Math. Theor.} {\bf 48} (2015), 255203.

\bibitem{miranda1994group}
    Miranda, H.\,F.,Thompson, R.\,C.,
    Group majorization, the convex hulls of sets of matrices, and the diagonal element-singular value inequalities,
    \emph{Linear Algebra Appl.} {\bf 199} (1994), 131.

\bibitem{modi2010unified}
    Modi, K. \emph{et al.},
    Unified view of quantum and classical correlations,
    \emph{Phys. Rev. Lett.} {\bf 104} (2010), 80501.

\bibitem{Nielsen2010}
    Nielsen, M.\,A., Chuang, I.\,L.,
    \emph{Quantum Computation and Quantum Information},
    Cambridge University Press, Cambridge 2010.

\bibitem{Hanche1984}
    Hanche-Olsen, H., St{\o}rmer, E., \emph{Jordan Operator Algebras},
    Pitman, London 1984.

\bibitem{Naber1992}
    Naber, G.\,L.,
    \emph{The Geometry of Minkowski Spacetime: An Introduction to the Mathematics of the Special Theory of Relativity},
    Springer, New York Dordrecht Heidelberg London 2012.

\bibitem{olkiewicz1999environment}
    Olkiewicz, R.,
    Environment-induced superselection rules in Markovian regime,
    \emph{Commun. Math. Phys.} {\bf 208} (1999), 245.

\bibitem{ollivier2001quantum}
    Ollivier, H., Zurek, W.\,H.,
    Quantum discord: a measure of the quantumness of correlations,
    \emph{Phys. Rev. Lett.} {\bf 88} (2001), 17901.

\bibitem{peres1996separability}
    Peres, A.
    Separability criterion for density matrices,
    \emph{Phys. Rev. Lett.} {\bf 77} (1996), 1413.

\bibitem{robertson1983schwarz}
    Robertson, A.\,G.,
    Schwarz inequalities and the decomposition of positive maps on C*-algebras,
    [w:] \emph{Mathematical Proceedings of the Cambridge Philosophical Society}
    {\bf 94} (1983), 291.

\bibitem{Rudin1991}
    Rudin, W.,
    \emph{Functional analysis},
    McGraw-Hill, New York 1991.

\bibitem{rutkowski2015class}
    Rutkowski, A., \emph{et al.},
    A class of bistochastic positive optimal maps in $M_{d}(\mathbb{C})$,
    \emph{arXiv preprint} (2015), arXiv:1505.07854.

\bibitem{Ryan2002}
    Ryan, R., \emph{Introduction to Tensor Products of Banach Spaces},
    Springer, Berlin Heidelberg New York 2002.

\bibitem{schrodinger1935gegenwartige}
    Schr{\"o}dinger, E.,
    Die gegenw{\"a}rtige Situation in der Quantenmechanik,
    \emph{Naturwissenschaften} {\bf 23} (1935), 823.

\bibitem{schwarz1955hausdorff}
    Schwarz, S.,
    On Hausdorff bicompact semigroups,
    \emph{Czechoslovak Math. J.} {\bf 5} (1955), 1.

\bibitem{stinespring1955positive}
    Stinespring, W.\,F.,
    Positive functions on C*-algebras,
    \emph{P. Am. Math. Soc.} {\bf 6} (1955), 211.

\bibitem{stormer2013decomposition}
    St{\o}rmer, E.,
    A decomposition theorem for positive maps, and the projection onto a spin factor,
    \emph{arXiv preprint} (2013), arXiv:1308.3332.

\bibitem{stormer1963positive}
    St{\o}rmer, E.,
    Positive linear maps of operator algebras,
    \emph{Acta Mathematica} {\bf 110} (1963), 233.

\bibitem{Stormer2013}
    St{\o}rmer, E.,
    \emph{Positive Linear Maps of Operator Algebras},
    Springer, Berlin Heidelberg New York 2013.

\bibitem{stormer2008separable}
    St{\o}rmer, E.,
    Separable states and positive maps,
    \emph{J. Funct. Anal.} {\bf 254} (2008), 2303.

\bibitem{stormer2009separable}
    St{\o}rmer, E.,
    Separable states and positive maps II,
    \emph{Math. Scand.} {\bf 105} (2009), 188.

\bibitem{straszewicz1935exponierte}
    Straszewicz, S.,
    {\"U}ber exponierte Punkte abgeschlossener Punktmengen,
    \emph{Fund. Math.} {\bf 24} (1935), 139.

\bibitem{Takesaki1}
    Masamichi, T., \emph{Theory of Operator Algebras}, t.\,1, Springer, Berlin Heidelberg New York 2003.

\bibitem{Takesaki2}
    Masamichi, T., \emph{Theory of Operator Algebras}, t.\,2, Springer, Berlin Heidelberg New York 2003.

\bibitem{Takesaki3}
    Masamichi, T., \emph{Theory of Operator Algebras}, t.\,3, Springer, Berlin Heidelberg New York 2003.

\bibitem{werner1989quantum}
    Werner, R.\,F.,
    Quantum states with Einstein-Podolsky-Rosen correlations admitting a hidden-variable model,
    \emph{Phys. Rev. A} {\bf 40} (1989), 4277.

\bibitem{woronowicz1976positive}
    Woronowicz, S.\,L.,
    Positive maps of low dimensional matrix algebras,
    \emph{Rep. Math. Phys.} {\bf 10} (1976), 165.

\bibitem{yngwason2005role}
    Yngvason, J.,
    The role of type III factors in quantum field theory,
    \emph{Rep. Math. Phys.} {\bf 55} (2005), 135.

\bibitem{Zhang2006}
    Zhang, F.,
    \emph{The Schur Complement and its Applications},
    Springer, Berlin Heidelberg New York 2006.

\end{thebibliography}

% Add a second set of references, if you wish...
%\renewcommand{\bibname}{Bibliografia 2}
%\begin{thebibliography}{99}
%
%\end{thebibliography}


% Print index and add to the table of content
%\chapter*{}
%\clearpage
%\addcontentsline{toc}{chapter}{Indeksy}
%\printindex{sym}{Indeks symboli}
%\printindex{idx}{Skorowidz}
